---
title: "RWorksheet_#5B"
author: "Berja,Bibit,Buenvenida"
date: "2024-11-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#The Error Is Still Unknown
```


```{r}
# Load necessary libraries
library(polite)
library(rvest)
library(dplyr)
library(purrr)
library(ggplot2)  # Load ggplot2 for plotting

# Function to scrape product reviews from a given product URL
scrape_product_reviews <- function(product_url) {
  # Create a polite session
  session <- bow(product_url, user_agent = "Educational")
  
  # Scrape the page
  page <- scrape(session)
  
  # Extract reviews
  reviews <- page %>%
    html_nodes(".review") %>%  # Adjust the selector based on actual HTML structure
    map_df(~ {
      tibble(
        Reviewer_Name = .x %>% html_node(".a-profile-name") %>% html_text(trim = TRUE),
        Review_Date = .x %>% html_node(".review-date") %>% html_text(trim = TRUE),
        Individual_Rating = .x %>% html_node(".a-icon-alt") %>% html_text(trim = TRUE),
        Review_Text = .x %>% html_node(".review-text-content span") %>% html_text(trim = TRUE),
        Review_Title = .x %>% html_node(".review-title") %>% html_text(trim = TRUE),
        Verified_Purchase = ifelse(grepl("Verified Purchase", .x %>% html_node(".review-title") %>% html_text(trim = TRUE)), TRUE, FALSE)
      )
    }) %>%
    slice(1:20)  # Limit to 20 reviews

  return(reviews)
}

# Function to scrape products from a given category URL
scrape_amazon_category <- function(category_url, category_name) {
  # Create a polite session
  session <- bow(category_url, user_agent = "Educational")
  
  # Scrape the page
  page <- scrape(session)
  
  # Extract product details
  products <- page %>%
    html_nodes(".s-main-slot .s-result-item") %>%
    map_df(~ {
      product_url <- .x %>% html_node("h2 a") %>% html_attr("href")  # Extract product URL
      product_url <- paste0("https://www.amazon.com", product_url)  # Complete the URL
      
      tibble(
        Title = .x %>% html_node("h2") %>% html_text(trim = TRUE),
        Price = .x %>% html_node(".a-price .a-offscreen") %>% html_text(trim = TRUE),
        Description = .x %>% html_node(".a-text-normal") %>% html_text(trim = TRUE),
        Rating = .x %>% html_node(".a-icon-alt") %>% html_text(trim = TRUE),
        Reviews = .x %>% html_node(".a-size-small .a-link-normal") %>% html_text(trim = TRUE),
        Category = category_name,  # Add category name here
        Product_URL = product_url  # Store product URL
      )
    }) %>%
    slice(1:20)  # Limit to 20 products

  # Scrape reviews for each product
  reviews_list <- map(products$Product_URL, scrape_product_reviews)
  
  # Combine products with their reviews
  products_with_reviews <- products %>%
    mutate(Reviews = reviews_list)  # Add reviews list to products

  return(products_with_reviews)
}

# Example category URLs (you need to adjust these)
categories <- list(
  fishing = 'https://www.amazon.com/s?k=fishing',
  electronics = 'https://www.amazon.com/s?k=electronics',
  books = 'https://www.amazon.com/s?k=books',
  home_kitchen = 'https://www.amazon.com/s?k=home+kitchen',
  clothing = 'https://www.amazon.com/s?k=clothing'
)

# Initialize an empty data frame to store all products
all_products <- tibble()

# Loop through categories and scrape 20 products from each
for (category_name in names(categories)) {
  category_url <- categories[[category_name]]
  category_products <- scrape_amazon_category(category_url, category_name)
  all_products <- bind_rows(all_products, category_products)
}

# Convert Price and Rating to numeric for analysis
all_products$Price <- as.numeric(gsub("\\$", "", gsub(",", "", all_products$Price)))
all_products$Rating <- as.numeric(gsub(" out of 5 stars", "", all_products$Rating))

# Display the extracted data ```r
print(all_products)

# Prepare data for bar plots
avg_price <- all_products %>%
  group_by(Category) %>%
  summarize(Average_Price = mean(Price, na.rm = TRUE))

avg_rating <- all_products %>%
  group_by(Category) %>%
  summarize(Average_Rating = mean(Rating, na.rm = TRUE))

# Create a bar plot for Average Price by Category using ggplot2
ggplot(avg_price, aes(x = reorder(Category, Average_Price), y = Average_Price)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  labs(title = "Average Price of Products by Category", 
       x = "Category", 
       y = "Average Price ($)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Create a bar plot for Average Rating by Category using ggplot2
ggplot(avg_rating, aes(x = reorder(Category, Average_Rating), y = Average_Rating)) +
  geom_bar(stat = "identity", fill = "lightgreen") +
  labs(title = "Average Ratings of Products by Category", 
       x = "Category", 
       y = "Average Rating (out of 5)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Rank products by Price
ranked_by_price <- all_products %>%
  group_by(Category) %>%
  arrange(Price) %>%
  mutate(Price_Rank = row_number())

# Rank products by Ratings
ranked_by_rating <- all_products %>%
  group_by(Category) %>%
  arrange(desc(Rating)) %>%
  mutate(Rating_Rank = row_number())

# Display the ranked data
print(ranked_by_price)
print(ranked_by_rating)
```

